statistical-analysis

### 2024-05-03 R/analysis-code/analysis.qmd
More README edits
Added script to exrtact libraries and versions for a list in the readme

# Define a more refined tuning grid for LASSO with a wider range of penalty values
tuning_grid_lasso <- expand.grid(
  penalty = 10^seq(-10, 1, length.out = 50)  # Increase the range and resolution of the penalty parameter
)

@@

# Tune the model using the refined tuning grid and increased folds
tuning_results_lasso <- tune_grid(
  lasso_workflow,
  resamples = cv_folds_continuous,
  grid = tuning_grid_lasso,
  metrics = metric_set(yardstick::rmse)
)

@@

# Fit the final model with the best hyperparameters on the full training dataset
final_fit_lasso <- fit(
  lasso_workflow %>% finalize_workflow(best_hps_lasso),
  data = train_data_continuous
)

@@

# Visualize the tuning results
autoplot(tuning_results_lasso)

```
### There still seems to be overfitting. The RMSE on the test set is higher than the training set.
### Additionally, LASSO models are not ideal for capturing non-linear relationships.
### We will try a different model

>>>>

# Define tuning grid for LASSO with a wide range of penalty values
tuning_grid_lasso <- expand.grid(
  penalty = 10^seq(-10, 1, length.out = 50)

@@

# Tune the model using the tuning grid and folds
tuning_results_lasso <- tune_grid(
  lasso_workflow,
  resamples = cv_folds_continuous,
  grid = tuning_grid_lasso,
  metrics = metric_set(yardstick::rmse)
)

@@

# Fit the final model with the best hyperparameters on the full training dataset
final_fit_lasso <- fit(
  lasso_workflow %>% finalize_workflow(best_hps_lasso),
  data = train_data_continuous
)
```

### Extract the fitted model and calculate RMSE for the training and testing sets
```{r}

@@

# Visualize the tuning results
autoplot(tuning_results_lasso)
```
### There still seems to be overfitting. The RMSE on the test set is higher than the training set.
### Additionally, LASSO models are not ideal for capturing non-linear relationships.
### We will try a different model
